An Empirical Analysis of the Benefits of Adaptive Gradient Methods

### 2017-12-04 Project/Presentation/main.tex
[WIP] added trivial functions in slides

\end{document}

>>>>

\section{Our work}
\begin{frame}{Our work}
\begin{itemize}
\item<2->{Implementation of Polyak's heavy ball method(CM), Adagrad, Adadelta, Adam, RMSprop, effectively creating a suite of first-order optimization methods.
          \begin{itemize}
          \item<2->{Implemented in NumPy\footfullcite{numpy}}
          \end{itemize}}
\item<3->{Analyzing behaviour of GD, CM, Adagrad, Adadelta, Adam, RMSprop on selected pathological test functions for optimization}
\item<4->{Experiments on Deep Neural Networks - Multi-layer perceptrons, Autoencoders and Generative Adversarial Networks\footfullcite{gan}}
\end{itemize}
\end{frame}

\subsection{Pathological Functions}
\begin{frame}{Functions which were used}
For our initial experiments, we chose 6 functions\footfullcite{test-funcs}:
\begin{itemize}
\item<1->{Bohachevsky's Functions 1, 2, 3}
\item<2->{Beale's Function}
\item<3->{Rosenbrock's Function}
\item<4->{Styblinsky-Tang's Function}
\end{itemize}
\end{frame}

\begin{frame}{Behaviour with Bohachevsky's Function 1}
\begin{equation}
\label{B1}
f(\xbold) = x_{1}^{2} + 2x_{2}^{2} - 0.3\cos(3\pi x_{1}) - 0.4\cos(4\pi x_{2}) + 0.7
\end{equation}
\end{frame}

\begin{frame}{Behaviour with Bohachevsky's Function 2}
\begin{equation}
\label{B2}
f(\xbold) = x_{1}^{2} + 2x_{2}^{2} - 0.3\cos(3\pi x_{1})\cos(4\pi x_{2}) + 0.3
\end{equation}
\end{frame}

\begin{frame}{Behaviour with Bohachevsky's Function 3}
\begin{equation}
\label{B3}
f(\xbold) = x_{1}^{2} + 2x_{2}^{2} - 0.3\cos(3\pi x_{1} + 4\pi x_{2}) + 0.3
\end{equation}
\end{frame}

\begin{frame}{Behaviour with Beale's Function}
\begin{equation}
\label{BL}
f(\xbold) = (1.5 - x_{1} + x_{1}x_{2})^{2} + (2.25 - x_{1} + x_{1}x_{2}^{2})^{2} + (2.625 - x_{1} + x_{1}x_{2}^{3})^{2}
\end{equation}
\end{frame}

\begin{frame}{Behaviour with Rosenbrock's Function}
\begin{equation}
\label{RB}
f(\xbold;a=1, b=25) = (1 - x_{1})^{2} + 25(x_{2} - x_{1})^{2}
\end{equation}
\end{frame}

\begin{frame}{Behaviour with Styblinsky-Tang's Function}
\begin{equation}
\label{ST}
\displaystyle f(\xbold;n=2) = \sum_{i=1}^{n=2} x_{i}^{2} - 16x_{i}^{2} + 5x_{i}
\end{equation}
\end{frame}
\end{document}
